Manuscript Preparation

### 2018-06-06 Houston/src/manuscript_preparation.Rmd
SVM kernel radial basis

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
options(scipen = 1, digits = 2)
require(dplyr)
require(ggplot2)
require(RcppRoll)
require(markovchain)
require(reshape)
require(survival)
require(caret)
require(e1071)
knitr::opts_knit$set(root.dir = "~/Documents/Projects/Github/CRIS/ViolationData/violation-data-analysis/") # !! CHANGE PATH TO MATCH YOUR OWN

# source("~/Documents/Projects/Github/CRIS/ViolationData/violation-data-analysis/Houston/src/prepare_violation.R")
# source("~/Documents/Projects/Github/CRIS/ViolationData/violation-data-analysis/Houston/src/roll_over.R")

# knitr::opts_knit$set(root.dir = "~/documents/projects/violation-data-analysis") # !! CHANGE PATH TO MATCH YOUR OWN

@@

svm.model <- svm(severe ~ 
                   last.quarter.lost+last.year.lost+last.three.years.lost
                 +last.quarter.restrict+last.year.restrict+last.three.years.restrict
                 +last.quarter.viol+last.year.viol+last.three.years.viol
                 +last.quarter.death+last.year.death+last.three.years.death,
                 data=labeled.data.lost.train, method="C-classification", kernel="linear")
summary(svm.model)

pred.train <- predit(svm.model, labeled.data.lost.train)
mean(pred.train==labeled.data.lost.train$severe)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
options(scipen = 1, digits = 2)
require(dplyr)
require(ggplot2)
require(RcppRoll)
require(markovchain) # FIX: markovchain seems not compatible with R3.5.0
require(reshape)
require(survival)
require(caret)
require(e1071)
# knitr::opts_knit$set(root.dir = "~/Documents/Projects/Github/CRIS/ViolationData/violation-data-analysis/") # !! CHANGE PATH TO MATCH YOUR OWN
# source("~/Documents/Projects/Github/CRIS/ViolationData/violation-data-analysis/Houston/src/prepare_violation.R")
# source("~/Documents/Projects/Github/CRIS/ViolationData/violation-data-analysis/Houston/src/roll_over.R")
#knitr::opts_knit$set(root.dir = "~/documents/projects/violation-data-analysis") # !! CHANGE PATH TO MATCH YOUR OWN

@@

svm.model <- svm(severe ~ 
                   last.quarter.lost+last.year.lost+last.three.years.lost
                 +last.quarter.restrict+last.year.restrict+last.three.years.restrict
                 +last.quarter.viol+last.year.viol+last.three.years.viol
                 +last.quarter.death+last.year.death+last.three.years.death,
                 data=labeled.data.lost.train, method="C-classification", kernel="radial")
summary(svm.model)

# save the computationally costly svm model
#save(svm.model, file="./Houston/data/svm_radial.RData")

plot(svm.model, labeled.data.lost.train)

compareTable <- table (labeled.data.lost.train$severe, predict(svm.model))  # tabulate
mean(labeled.data.lost.train$severe != predict(svm)) # false rate

pred.train <- predict(svm.model, labeled.data.lost.train)
mean(pred.train==labeled.data.lost.train$severe) # true rate
```
